Supplementary Information

### 2020-08-31 doc/manuscript/MEE_manuscript.Rmd
fix name spellings

Kristina J. Anderson-Teixeira^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez,
Taia Awada,
Jennifer Baltzar,
Patrick Baker,
Sarayudh Bunyavejchewin,
Paulo Cherubini,
Justin Cooper,
Stuart Davies^2^,
Ryan Helcoski^1^,
Vasickova Ivana,
Kaspar Jakub,
Kamil Kral,
James Lutz,
Ellis Q. Margolis,
Justin Maxwell,
Sean McMahon^2^,
Helene Muller-Landau^2^,
Samonil Pavil,
Sabrina Russo,
Anastasia Sniderhan,
Alan J. Tepley^1,#^,
Mart Vlam,
Peter Zuidema

>>>>

Kristina J. Anderson-Teixeira^1,2^*,
Valentine Herrmann^1^,
Christy Rollinson^3^,
Bianca Gonzalez^1^,
Erika B. Gonzalez-Akre^1^,
Neil Pederson^4^,
Camille Piponiot^1,2^,
Ross Alexander,
Craig D. Allen,
Raquel Alfaro-Sánchez,
Tala Awada,
Jennifer Baltzar,
Patrick Baker,
Sarayudh Bunyavejchewin,
Paolo Cherubini,
Justin Cooper,
Stuart Davies^2^,
Ryan Helcoski^1^,
Vasickova Ivana,
Kaspar Jakub,
Kamil Kral,
James Lutz,
Ellis Q. Margolis,
Justin Maxwell,
Sean McMahon^2^,
Helene Muller-Landau^2^,
Samonil Pavil,
Sabrina Russo,
Anastasia Sniderhan,
Alan J. Tepley^1,#^,
Mart Vlam,
Peter Zuidema
